Trees

### 2019-02-07 R/Trees_making.Rmd
updated file subdirectories and minor formatting fixes

```{r list birds load} 
birds <- unique(read.csv("bird_list.csv")$species_name) #load our list of bird species and make the names unique
birds_stree <- read.tree("Ericson.tre") #load bird supertree
birds_stree #9993 tips = species
# str(birds_stree) # ypu can see this tree has edge (branch) lengths

@@

write.tree(tree, file="tree_curtis1998.tre") #save the tree in Newick format, if needed
# read.tree(file="tree_curtis1998.tre") #if you need to read it
```

@@

```{r check Curtis1998 tree binary}
is.binary.tree(tree) #FALSE (i.e. there are polytomies)
# is.ultrametric(tree) #the tree has no branch lengths, so cant be checked
write.tree(tree, file="tree_curtis1998.tre") #save the tree
# tree <- read.tree(file="tree_curtis1998.tre") #if you need to read it
```

@@

```{r resolve Curtis1998 polytomies at random}
set.seed(111) #making it replicable
tree_random <- multi2di(tree,random=TRUE)
is.binary.tree(tree_random) #TRUE
write.tree(tree_random, file="tree_curtis1998_random.tre") #save the tree
# tree_random <- read.tree(file="tree_curtis1998_random.tre") #if you need to read it
```

@@

If downloading from R treebase did not work, upload tree saved in a file:
```{r dwonload one tree from file, eval = FALSE}
Acers_tree <- read.nexus(file = "T418.nex") #read Nexus tree file
```

>>>>

```{r list birds load} 
birds <- unique(read.csv("../data/bird_list.csv")$species_name) #load our list of bird species and make the names unique
birds_stree <- read.tree("../data/Ericson.tre") #load bird supertree
birds_stree #9993 tips = species
# str(birds_stree) # ypu can see this tree has edge (branch) lengths

@@

# write.tree(tree, file="../data/tree_curtis1998.tre") #save the tree in Newick format, if needed
# read.tree(file="../data/tree_curtis1998.tre") #if you need to read it
```

@@

```{r check Curtis1998 tree binary}
is.binary.tree(tree) #FALSE (i.e. there are polytomies)
# is.ultrametric(tree) #the tree has no branch lengths, so cant be checked
#write.tree(tree, file="../data/tree_curtis1998.tre") #save the tree
# tree <- read.tree(file="../data/tree_curtis1998.tre") #if you need to read it
```

@@

```{r resolve Curtis1998 polytomies at random}
set.seed(111) #making it replicable
tree_random <- multi2di(tree,random=TRUE)
is.binary.tree(tree_random) #TRUE
#write.tree(tree_random, file="../data/tree_curtis1998_random.tre") #save the tree
# tree_random <- read.tree(file="../data/tree_curtis1998_random.tre") #if you need to read it
```

@@

If downloading from R treebase did not work, upload tree saved in a file:
```{r dwonload one tree from file, eval = FALSE}
Acers_tree <- read.nexus(file = "../data/T418.nex") #read Nexus tree file
```
